### 2013-12-09 fig_arfi_segs.tex
added Zach's methods and figures; still need to refine

\begin{figure}[htb!]
\centering
\begin{tabular}{c}
\includegraphics[width=1.0\textwidth]{figs/Bmode_CapsuleSegs.eps} \\
\includegraphics[width=1.0\textwidth]{figs/ARFI_CGsegs.eps} \\
\end{tabular}
\caption{Representative B-mode (top row) and ARFI images (bottom row), with
    superimposed segmentation outlines of the capsule and CG, respectively, for
    the same study subject shown in Figure~\ref{fig:mr_segs_vol}.  The B-mode
    images were segmented in the axial view, using the hypoechoic border of the
    capsule.  Notice that for large prostates, like the one shown in this
    figure, that the edges of the organ were not always captured in the imaging
    field-of-view.  The CG in the ARFI images was typically segmented using the
    coronal view, which, especially in the presence of extensive BPH, can have
    a very characteristic, heterogeneous appearance.  It should be noted that
    the coronal views in these ultrasound images are flipped 180\degree relative
    to the same images in Figure~\ref{fig:mr_segs_vol}.}
\label{fig:arfi_segs} 
\end{figure}

>>>>

\begin{figure}[htb!]
\centering
\begin{tabular}{c}
%\includegraphics[width=1.0\textwidth]{figs/Bmode_CapsuleSegs.eps} \\
%\includegraphics[width=1.0\textwidth]{figs/ARFI_CGsegs.eps} \\
\includegraphics[width=0.8\textwidth]{zach/us_capsule_seg_model.png} \\
\includegraphics[width=0.8\textwidth]{zach/arfi_central_seg.png} \\
\includegraphics[width=0.8\textwidth]{zach/us_central_seg_model.png} \\
\end{tabular}
\caption{TOP ROW: B-mode capsule segmentation using all three orthogonal
    planes.  The primary segmentation plane is sagittal (second pane), however
    the axial (first pane) and coronal (third pane) are used to guide this
    segmentation because as the label map is built up, the intersections of
    the label map in the axial and sagittal planes can be viewed as well. The
    block-like character of the axial/coronal sections of the label map are a
    direct result of downsampling.  MIDDLE ROW: ARFI central gland segmentation
    (blue) with the capsule model (pink) overlaid for guidance during
    segmentation.  BOTTOM ROW: Demonstrates the modeled capsule with slice
    intersections on the axial, sagittal, and coronal planes respectively (all
    pink). This model was built up from the label map created in the B-mode
    capsule segmentation.}
\label{fig:arfi_segs} 
\end{figure}

### 2013-12-09 image_proc_methods.tex
added Zach's methods and figures; still need to refine

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG and urethra, PZ and AFS were
segmented independently according to their well-established anatomical
characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location (Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG
segmentation. Although not readily visible on every case, the AFS was
identified by its low T2 signal intensity and its location anterior to the
central gland.

@@

ARFI images were segmented using a similar procedure to the MR images.  B-mode
images were used to segment the prostate capsules since contrast between the
peripheral zone and the periprostatic fat can be low, and poor displacement SNR
can be present along the anterior aspect of the prostate in ARFI images, making
it difficult to delineate that boundary.  The central gland was segmented as a
stiffer region, relative to the peripheral zone, in the center of the prostate.

@@

The 3D slicer models were used to render volume estimates of the PZ and CG,
with the sum of PZ and CG representing the total prostate gland volume.  AFS
volume estimates in select MR cases were included in the total prostate gland
volume estimates.  Orthogonal tri-axial measurements in the lateral-to-lateral,
axex-to-base, and anterior-to-posterior dimensions were made in 3D slicer.

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
\subsubsection{MR Image Segmentation and Modeling}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG and urethra, PZ and AFS were
segmented independently according to their well-established anatomical
characteristics on
T2WI.~\cite{Barentsz2012,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location (Figure~\ref{fig:mr_anatomy}). The urethra was included in the CG
segmentation. Although not readily visible on every case, the AFS was
identified by its low T2 signal intensity and its location anterior to the
central gland.

The 3D models were used to render volume estimates of the PZ and CG, with the
sum of PZ and CG representing the total prostate gland volume. AFS volume
estimates in select MR cases were included in the total prostate gland volume
estimates. Orthogonal tri-axial measurements in the lateral-to-lateral,
apex-to-base, and anterior-to-posterior dimensions were made in slicer by
placing an ROI cube in the model's center and expanding the ROI cube to fit the
maximal model dimensions.

@@

\subsubsection{Ultrasound Image Segmentation and Modeling}
Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D Slicer
using the \verb+draweffect+ tool to model and measure the prostate capsule and CG
volume and tri-axial dimensions.  The sagittal imaging plane was chosen for
segmentation because it has a greater number of easily identifiable anatomical
structures:  seminal vesicles in the left and right posterior base, urethra in
the mid apex, surrounding fibromuscular tissue in the anterior , and rectum in
the posterior  than either the axial or coronal views. Prostate capsule was
segmented in B-mode as this modality offers both high contrast between
prostatic tissue and surrounding periprostatic fat, and better SNR in the
anterior capsule region than ARFI images. ARFI was used to segment central gland as
there is clear delineation in this modality between central gland and
peripheral zone. This delineation is a result of the greater density of
connective tissue within the central gland versus the peripheral zone meaning
the central gland is stiffer than the surrounding peripheral zone.  Prior to
segmentation, both the B-mode and ARFI image stacks were downsampled along the
sagittal axis by a factor of 20 (i.e., from 360 slices per image stack to 18
slices per image stack). This was done because segmenting 360 slices per image
is inordinately time intensive, and does not improve the quality of the 3D
rendered model any more than segmenting the more reasonable 18 slices per image
stack. The parameters used for the resample scalar volume tool are shown below:

WHAT GOES HERE?

Although, segmentations were performed along the sagittal plane, label map
intersections in the axial and coronal views were used during active creation
of the sagittal segmentation to further improve segmentation accuracy.  This
was done by using the resampled image stack, B-mode for capsule and ARFI for
CG, as the background in the sagittal plane, and the original image stack as
background in the axial and coronal planes. All three orthogonal views were set
to the label map assigned to the resampled volume. The B-mode derived capsule
was segmented and modeled before the central gland. Parameters used for 3D
model rendering were identical to those used in table X for MR modeling. The
modeled capsule  helprf guide the CG segmentation by enabling capsule model
intersections in the three orthogonal planes during CG segmentation. The
capsule provided an outer boundary for the CG segmentation. The capsule and CG
models were then measured identically to the MR measurement procedure.

@@

\input{fig_roi_tool}
